FinalManuscript_DISCS_UG

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Final edits

\section{Related Work and Previous Implementations}

@@

This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosystems have yet to be implemented for image processing operations.

>>>>

\section{Previous Implementations of Secure Facial Recognition}

@@

%This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosystems have yet to be implemented for image processing operations.

### 2018-10-07 parts/03_methodology.tex
Final edits

\subsection{Evaluating Image Quality for Intensity Transformations}
In this section, we discuss the image quality metrics we will use for assessing the performance of non-linear intensity transformations.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up?

\section{Summary}
In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

>>>>

\subsection{Image Quality of Intensity Transformations}
In this section, we discuss the image quality metrics we will use for assessing the performance of non-linear intensity transformations.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up?
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.

Haar cascades will be implemented using homomorphic operations for facial detection.

Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
\section{Summary}
In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}
